---
title: "Statistical issues in the analysis of Illumina data"
output: html_notebook
---


## Introduction

In this document we show how to import the data for the BMC Bioinformatics paper [Statistical issues in the analysis of Illumina data](https://bmcbioinformatics.biomedcentral.com/articles/10.1186/1471-2105-9-85). We will be using the `beadarray` R package.


```{r message = FALSE}
library(beadarray)
```


```{r}
targets <- read.delim("spike_targets.txt",sep=" ",stringsAsFactors = FALSE)
targets
```

The raw data have been compressed into `.bab` files using the [`BeadDataPackR`](http://europepmc.org/articles/PMC2956622/) bioconductor tool. 

```{r echo=FALSE}
bld <- readIllumina(dir="data",sectionNames = as.character(targets$ArrayNo))
```

Summarize into bead summary data. No annotation conversion is performed, and the two strips are kept separate at this stage

```{r}
bsd <- summarize(bld,useSampleFac = FALSE)
```

`bsd` has many similarities with standard Bioconductor objects

```{r}
bsd
```

A boxplot highlight the difference between well-annotated probes (odd-numbered strips), and probes that are less well-annotated (even strips)

```{r}
boxplot(exprs(bsd)[,1:12])
```

Read the spike probe concentrations from the targets file and save in the object

```{r}

targets <- read.table("spike_targets.txt",header=TRUE)
pData(bsd)$SpikeConc <- targets$SpikeConc
pData(bsd)
```

